A Survey of Quantitative Descriptions of Molecular Structure

### 2012-03-20 paper.tex
Added some text around topological descriptors

>>>>

Broadly, one can classify descriptors based on the nature of
structural information they require. Constitutional descriptors only
require atom and bond labels and usually represent counts of different
types of atoms or bonds. While very simplistic they can play a useful
role in a variety of applications ranging from summaries of
physicochemical properties to predictive modeling
\cite{Bender:2005aa}.

Topological descriptors take into account connectivity along with atom
and bond labels. These descriptors essentially consider the molecule
as a labeled graph and characterize it using graph invariants. In
addition to graph invariants, topological descriptors based on
information theory such as entropy \cite{Dehmer:2009uq}. An advantage
of these descriptors is that do not require any intensive
pre-processing steps such as 3D coordinate generation and
conformational analysis. In addition, many graph invariants can be
rapidly computed for graphs corresponding to small molecule structures
(even though they may be computationally intractable on much larger
graphs). While this class of descriptors have been used extensively in
predictive modeling applications [REFS], a key drawback is their lack
of interpretability. Given the abstract nature of the many graph
invariants and information theoretic descriptors, their use in
predictive models makes it difficult to explain the model in simple
physicochemical terms.
